% resume.tex
% Use res.cls
\documentclass[line,margin]{res}

\usepackage{helvetica}
\usepackage{hyperref}

\begin{document}

% Header
\name{Matthew McFarland}
\address{\textit{\small{matmcfarland@gmail.com \\ https://github.com/vanetix}}}

% beginning of the actual resume
\begin{resume}

% Work Experience
\section{Experience}
\textit{\textbf{DevOps Engineer}} \hfill June 2016 - Present \\
Red Ventures (Formerly CreditCards.com)
\begin{itemize} \itemsep -2pt
  \item Transformed many disparate deployment methodologies into a well oiled Docker pipeline with a set of strong standards to facilitate fast iteration.
  \item Provided a key vision, developed, and deployed an application that capitalized this new pipeline to allow end developers to ship their code to multiple environments.
  \item Automated infrastructure creation and compliance with ansible and chef.
  \item Monitored AWS account compliance with custom Lambda functions.
\end{itemize}
\textit{\textbf{Software Developer}} \hfill June 2013 - July 2016 \\
Texas School Safety Center, Texas State University, San Marcos
\begin{itemize} \itemsep -2pt
  \item Developed and maintained various internal and external facing applications for use across Texas.
  \item Developed and maintained tools for administration of the Texas School Safety Center's production applications. (grunt-carpenter, passport-txssc)
  \item Managed all server configurations for production applications.
\end{itemize}
\textit{\textbf{Student Developer}} \hfill October 2011 - May 2013 \\
Texas School Safety Center, Texas State University, San Marcos
\begin{itemize} \itemsep -2pt
  \item Developed and maintained various open source libraries including (TrapperKeeper, grunt-includes, omniauth-txssc).
  \item Developed and maintained statewide and internal web applications built upon our open source libraries (TxSSC Ticket-System, TxSSC Dashboard, TEP Database).
\end{itemize}

% Education
\textit{\textbf{Bachelor of Arts, Computer Science}} \\
Texas State University, San Marcos

% Skills
\section{Skills}

\textit{\textbf{Technologies:}} \\
\begin{tabular}{l l l l}
  Docker & redis & PostgreSQL & Phoenix \\
  Nginx & Terraform & HAProxy & MySQL \\
  node.js & Ember & git & Ansible
\end{tabular}

\textit{\textbf{Languages:}} \\
\begin{tabular}{l l l l}
  Elixir & erlang & Javascript & Ruby \\
  Golang & Java & bash
\end{tabular}

\textit{\textbf{Key Interests:}} \\
\begin{tabular}{l l l }
  AWS & Elixir \\
  graphql & Kubernetes \\
  Scaling Infrastructure
\end{tabular}
% End of skills

% Open source projects
\section{Open source}

\textit{\textbf{elixir-keycloak}} - https://github.com/vanetix/elixir-keycloak \\
A OAuth2 strategy for the \href{https://www.keycloak.org}{Keycloak} the authorization server.

\textit{\textbf{grunt-includes}} - https://github.com/vanetix/grunt-includes \\
Plugin for the grunt(gruntjs.com) build system. Used to include file partials and assist in rapid development.

  % End of resume
\end{resume}
\end{document}
